---
title: "Random Forest: Dipeptide Numerical Analysis"
author: "Matthew Curcio"
date: "August 31, 2017"
output: html_document
---


## Introduction  

text

This work can be found on [GitHub](https://github.com/mccurcio/random_forest_dk_project) and on [RPubs](http://rpubs.com/oaxacamatt/Random_Forest_Oxygen_Binders).

### Protein classes:

0. Homo sapiens proteins - reviewed
1. [Erythrocruorin](https://en.wikipedia.org/wiki/Erythrocruorin)
2. [Hemerythrin](https://en.wikipedia.org/wiki/Hemerythrin)
3. [Hemocyanin](https://en.wikibooks.org/wiki/Structural_Biochemistry/Hemocyanin)
4. [Leghemoglobin](https://en.wikipedia.org/wiki/Leghemoglobin)
5. [Myoglobin](https://en.wikipedia.org/wiki/Myoglobin)
6. [Hemoglobin](https://en.wikipedia.org/wiki/Hemoglobin)


### Produce AA matrix:

Column 1 = Protein Class (0:6)  
Column 2 = Total AA per protein  
Columns 3:22; (G, P, A, V, L, I, M, C, F, Y, W, H, K, R, Q, N, E, D, S, T)  


?? found in hemoglobin file line six: aa = 1156
sp|Q86VB7|C163A_HUMAN Scavenger receptor cysteine-rich type 1 protein M130 OS=Homo sapiens GN=CD163 PE=1 SV=2

```{r libraires}
suppressMessages(library(seqinr))
suppressMessages(library(stringr))
suppressMessages(library(readr))
suppressMessages(library(randomForest))
suppressMessages(library(dplyr))

# devtools::install_github("MI2DataLab/randomForestExplainer")
suppressMessages(library(randomForestExplainer))
```

===================================================

# Preparation of Dipeptides and Numerical Analysis

===================================================

The section below writes empty files such that data can appended later.
```{r prepare_file}
prepare_col_titles <- function(protein_class) {
    UNIPROT_DIR = "~/Dropbox/git_projects/random_forest_dk_project/uniprot_1"
    setwd(UNIPROT_DIR)
    prefix_cols = c("class", "total_aa")
    peptides = c( "G", "P", "A", "V", "L", "I", "M", "C", "F", "Y",
                  "W", "H", "K", "R", "Q", "N", "E", "D", "S", "T")
    l <- c(prefix_cols, peptides)
    # Add DIPEPTIDES column titles
    for (i in 1:20) {
        for (j in 1:20) {
            l <- c(l, paste(peptides[i], peptides[j], sep = ""))
        }
    }
    # open/write/save dipeptide file for later appendix
    file_name = paste("dipeptide_class", protein_class, ".csv", sep = "")
    write(l, file = file_name, ncolumns = 422, sep = ",")
}

write_empty_files <- function() {
    for (i in 0:6) {
        prepare_col_titles(protein_class = i)
    }
}

# RUN
write_empty_files()
# END

```


```{r read_seq_2_numerical}

read_seq_txt_2_numerical <- function() {
    UNIPROT_DIR = "~/Dropbox/git_projects/random_forest_dk_project/uniprot_1"
    setwd(UNIPROT_DIR)
    o2_seqs = list.files(pattern = ".txt$")
    for (i in 1:7) {
        df = read.csv(file = o2_seqs[i], header = FALSE)
        df %>% mutate_if(is.factor, as.character) -> df
        aa_nums = prepare_monopeptide_percent(df, protein_class = (i-1))
        aa_nums = t(aa_nums)
        prepare_dipeptide_percent(df, protein_class = (i-1), aa_nums)
    }
}

# Begin Calculation of Percent MONO-peptides AND DI-peptides
read_seq_txt_2_numerical()
# END

```

### Prepare MONOPEPTIDE Percent

```{r prepare_monopeptide_percent}

prepare_monopeptide_percent <- function(df, protein_class) {
    peptides = c("G", "P", "A", "V", "L", "I", "M", "C", "F", "Y",
                 "W", "H", "K", "R", "Q", "N", "E", "D", "S", "T")
    aa_nums = as.vector(matrix(0, ncol = 22))
    for (row in seq(length(df))) {
        # First column is protein_class
        aa_nums[1] = protein_class
        # Second column is total number of amino acids
        total_aa = nchar(df[1, row])
        aa_nums[2] = total_aa
        # Column 3:22 - Calculate percent AA
        for (i in 1:20) {
            aa_nums[i + 2] = str_count(df[1, row], peptides[i]) / total_aa
        }
    }
    return(aa_nums)
}


```

### Prepare DIPEPTIDE Percent

```{r prepare_dipeptide_percent}

prepare_dipeptide_percent <- function(df, protein_class, aa_nums) {
    peptides = c("G", "P", "A", "V", "L", "I", "M", "C", "F", "Y",
                 "W", "H", "K", "R", "Q", "N", "E", "D", "S", "T")
    for (row in seq(length(df))) {
        # Column 22:422 - Calculate Dipeptide percent
        l <- aa_nums
        k = 1
        for (i in 1:20) {
            for (j in 1:20) {
                dipep = paste(peptides[i], peptides[j], sep = "")
                total_aa = nchar(df[1, k])
                b = str_count(df[1, row], peptides[i]) / total_aa
                l <- c(l, b)
                k =+ 1
            }
        }
        # Append vector of AA values
        file_name = paste("dipeptide_class", protein_class, ".csv", sep = "")
        write(aa_nums, file = file_name, append = TRUE, ncolumns = 422, sep = ",")
    }
}


```

