---
title: "Boruta-Dim-Redux"
author: "MCC"
date: "8/30/2019"
output: html_document
---

Title:

Libraries  
```{r message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)

Libraries = c("doMC", "knitr", "Boruta", "readr")

for(p in Libraries){  # Install if not present
    if(!require(p, character.only = TRUE)) { install.packages(p, dependencies = T) }
    library(p, character.only = TRUE)
}
```

Import data
```{r message=FALSE, warning=FALSE}
cancer_human_comps <- read_csv("../1data/cancer_human_comps.csv",
                               col_types = cols(Class = col_factor(levels = c("0","1")), 
                                                PID = col_character()))
#View(cancer_human_comps)

colnames(cancer_human_comps)[244] <- "NA" 
```
First Boruta run; ntree = 50, mtry = 2
```{r, cache=TRUE}
cancer_human_Active <- cancer_human_comps[, c(1, 4:423)]

registerDoMC(cores = 3) # Start multi-processor mode
start_time <- Sys.time() # Start timer

set.seed(1000)
Boruta_cancer_human_Active <- Boruta(Class ~ ., data = cancer_human_Active, doTrace = 1, mtry = 2, ntree = 500)

registerDoSEQ() # Stop multi-processor mode
Sys.time() - start_time  # Display       time difference
```
Show Model Info
```{r}
Boruta_cancer_human_Active
```

```{r fig.width=7.25}
plot(Boruta_cancer_human_Active)
```

Get Formula
```{r}
getConfirmedFormula(Boruta_cancer_human_Active)
```

Results from **Boruta_cancer_human_Active**

- Class ~ A + C + D + E + F + G + H + K + L + N +                 #10
          Q + R + S + T + V + Y + AA + AD + AE + AF + 
          AG + AI + AL + AM + AP + AR + AT + AV + AY + CA +
          CC + CE + CF + CG + CI + CK + CL + CN + CP + CQ + 
          CR + CS + CV + CY + DA + DC + DD + DG + DK + DP +       #50
          DQ + DR + DS + DW + EA + EC + EE + EK + EN + ES +     
          FA + FC + FK + FL + FT + GA + GC + GD + GG + GL +      
          GR + GT + GV + HC + HK + HS + IA + ID + IG + KC +         
          KD + KE + KF + KH + KK + KN + KQ + KR + KS + KY +       
          LA + LC + LE + LH + LL + LQ + LS + ME + `NA` + NC +     #100
          NI + NK + NS + PA + PC + PD + PS + PT + PV + QC +      
          QE + QK + QL + RA + RD + RE + RI + RK + RM + SA +      
          SC + SE + SK + SL + SP + SQ + SS + ST + TA + TC +      
          TD + TG + TK + TS + TT + TV + VA + VC + YA + YC +       #140
          YF + YL                                                 #142


Results: Keep 142 attributes listed above and dismiss the rest.


```{r}
post_boruta_dataset <- cancer_human_Active[, c("A", "C", "D", "E", "F", "G", "H", "K", "L", "N", "Q", "R", "S", "T", "V", "Y", "AA", "AD", "AE", "AF", "AG", "AI", "AL", "AM", "AP", "AR", "AT", "AV", "AY", "CA", "CC", "CE", "CF", "CG", "CI", "CK", "CL", "CN", "CP", "CQ", "CR", "CS", "CV", "CY", "DA", "DC", "DD", "DG", "DK", "DP", "DQ", "DR", "DS", "DW", "EA", "EC", "EE", "EK", "EN", "ES", "FA", "FC", "FK", "FL", "FT", "GA", "GC", "GD", "GG", "GL", "GR", "GT", "GV", "HC", "HK", "HS", "IA", "ID", "IG", "KC", "KD", "KE", "KF", "KH", "KK", "KN", "KQ", "KR", "KS", "KY", "LA", "LC", "LE", "LH", "LL", "LQ", "LS", "ME", "NA", "NC", "NI", "NK", "NS", "PA", "PC", "PD", "PS", "PT", "PV", "QC", "QE", "QK", "QL", "RA", "RD", "RE", "RI", "RK", "RM", "SA", "SC", "SE", "SK", "SL", "SP", "SQ", "SS", "ST", "TA", "TC", "TD", "TG", "TK", "TS", "TT", "TV", "VA", "VC", "YA", "YC", "YF", "YL")]
```










