---
title: "Corrplot    "
author: "MCC"
date: "8/31/2019"
output: html_document
---

Libraries  
```{r message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)

#import java.util.List ?

Libraries = c("doMC", "readr", "ggplot2", "corrplot", "caret")

# Load Libraries
for(p in Libraries){ library(p, character.only = TRUE) }

# registerDoMC(cores = 3) # Start multi-processor mode
# registerDoSEQ() # Stop multi-processor mode
```

Import data
```{r message=FALSE, warning=FALSE}
cancer_human_comps <- read_csv("../1data/cancer_human_comps.csv",
                               col_types = cols(Class = col_factor(levels = c("0","1"))))
#View(cancer_human_comps)
#head(cancer_human_comps)

colnames(cancer_human_comps)[244] <- "NA" 

cancer_human_Active <- cancer_human_comps[, c(4:423)]
```

Correlation Matrix for 423 features. 
```{r fig.height=7, fig.width=7}
cancer_human_Active_scale <- scale(cancer_human_Active, center = TRUE, scale = TRUE)

corr_matrix <- cor(cancer_human_Active_scale)

corrplot(corr_matrix, 
         # order = "hclust", # With out hclust, we see order as in df.
         type = "lower",
         addgrid.col = "NA")
```

After inspecting the correlation matrix, we set the correlation threshold at 0.75.

Filtered crrelation matrix for 423 features. 
```{r fig.height=7, fig.width=7}
highly_corr <- findCorrelation(corr_matrix, 0.75, verbose = TRUE)

# Remove all the variables correlated greater than 0.75.
corr_matrix_filtered_scaled <- cancer_human_Active_scale[, -highly_corr]
corr_matrix_f_s <- cor(corr_matrix_filtered_scaled)

corrplot(corr_matrix_f_s, 
         # order = "hclust", # With out hclust, we see order as in df.
         type = "lower",
         addgrid.col = "NA")
```

### Results: 

There is significant correlation between eight of the 423 features to a degree greater than 0.75.

- Combination row 1 and column 21 is above the cut-off, value = 0.86 
    - column 1 = "A", column 21 = "AA"
- Combination row 2 and column 42 is above the cut-off, value = 0.795 
    - column 2 = "C", column 42 = "CC"
- Combination row 13 and column 273 is above the cut-off, value = 0.773 
    - column 13 = "P", column 273 = "PP"
- Combination row 16 and column 336 is above the cut-off, value = 0.788 
    - column 16 = "S", column 336 = "SS"















