---
title: "Anti-cancer peptides convert to AAC & DPC"
author: "MCC"
date: "8/26/2019"
output: html_document
---

Title: Anti-cancer peptides convert to AAC & DPC

######
**Column Name Information**

* Column 1 = Protein ID(PID) = {A1, ..., C905} 
    * A1-A905 <- anti-cancer-peptide followed by number
    * C1-C905 <- control followed by number
* Column 2 = anti-cancer Class {0:1}  
    * class = 0 <- control proteins
    * class = 1 <- anti-cancer proteins from UniProt
* Column 3 <- TotalAA per protein  
* Columns 4:23 <- AAC(A, C, D, E, F, G, H, I, K, L, M, N, P, Q, R, S, T, V, W, Y)  
* Columns 24:423 <- Di-peptide Compositions(AA, ... , YY)  

**Needed to produce percent composition from list of 'anti-cancer-peptides'**

df <- list of proteins
file_name <- {"anti_cancer_comps.csv", "control_comps.csv"}
col_names <- matrix('character', 1, 423)
anti_cancer_class <- {0, 1}
PID_letter <- 'string' = {"A" for Anti-cancer-peptide; "C" for Control-protein}
######

Libraries  
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)

Libraries = c("knitr", "seqinr", "stringr")

for(p in Libraries){ library(p, character.only = TRUE) }
```
Import data
```{r}
anticancer <- read.fasta(file = "uniprot-anti+cancer+peptide.fasta",
                         seqtype = "AA", 
                         as.string = TRUE,
                         seqonly = TRUE)
```
Create peptide names
```{r}
create_peptide_names <- function(){
    AA1 <- c("A", "C", "D", "E", "F", "G", "H", "I", "K", "L", 
             "M", "N", "P", "Q", "R", "S", "T", "V", "W", "Y")
    # Produce dipeptide names
    dp_names <- array(0, 400)
    n = 1
    for (i in 1:20) {
        for (j in 1:20) {
            dp_names[n] <- paste(AA1[[i]], AA1[[j]], sep = "")
            n = n + 1
        }
    }
    peptide_names <- c(AA1, dp_names)
}

peptide_names <- create_peptide_names()
is.character(peptide_names)
```
Construct column names for files
```{r}
create_col_names <- function(peptide_names){
    info <- c("PID", "Class", "TotalAA")
    col_names <- c(info, peptide_names)
}

col_names <- create_col_names(peptide_names)
is.character(col_names)
```
Prepare csv file
```{r}
file_name = "anti_cancer_comps.csv"

Prepare_csv_file <- function(file_name, col_names) {
     write.table(t(col_names),
                 file_name,
                 sep = ",",
                 append = TRUE,
                 col.names = FALSE, 
                 row.names = FALSE, 
                 eol = "\n")
}

Prepare_csv_file(file_name, col_names)                        
```


### Prepare MONO_DI_PEPTIDE Percents

```{r echo=TRUE, message=FALSE, warning=FALSE}
#anticancer  # df = anticancer; See: Import data
Class = 1
PID_letter = "A"
#peptide_names # chr[1:420] c(AA1, dp_names) See: create_peptide_names()
file_name = "anti_cancer_comps.csv"

calc_1_2_peptide_per_comps <- function(anticancer, Class, PID_letter, peptide_names, file_name) {
    aa_nums = array(0, dim = 423)
    for (i in seq(length(anticancer))) {
        # 1st column is class
        aa_nums[1] = Class
        # 2nd column = total number of AA per seq
        total_aa = nchar(anticancer[i])
        aa_nums[2] = total_aa
        # 3rd column = PID unique id
        aa_nums[3] = paste(PID_letter, i, sep = "")
        # Columns 4:423 - Calculate percent composition
        for (j in 1:420) {
            aa_nums[j+3] = str_count(anticancer[i], pattern = peptide_names[j]) / total_aa
        }
        # Append aa_nums vector to file_name
        write.table(t(aa_nums), file_name, row.names = F, col.names = F, append = T, sep = ",", eol = "\n")
    }
}

calc_1_2_peptide_per_comps(anticancer, Class, PID_letter, peptide_names, file_name) 
```


