---
title: "PCA-Dim-Redux"
author: "MCC"
date: "8/30/2019"
output: html_document
---

Libraries  
```{r message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)

Libraries = c("doMC", "readr", "ggplot2")

# Load Libraries
for(p in Libraries){ library(p, character.only = TRUE) }

# registerDoMC(cores = 3) # Start multi-processor mode
# registerDoSEQ() # Stop multi-processor mode
```

Import data
```{r message=FALSE, warning=FALSE}
cancer_human_comps <- read_csv("../1data/cancer_human_comps.csv",
                               col_types = cols(Class = col_factor(levels = c("0","1"))))
#View(cancer_human_comps)
#head(cancer_human_comps)

colnames(cancer_human_comps)[244] <- "NA" 

cancer_human_Active <- cancer_human_comps[, c(4:423)]
```

```{r}
pca_info = prcomp(cancer_human_Active, rank. = 25) # rank. limits output to top 25 principle components

#pca_info # Very large

summary(pca_info)
```

```{r}
names(pca_info)
```
```{r}
str(pca_info)
```

```{r}
plot(pca_info$sdev[1:40],
     main = "Plot: Top 40 Std Dev From PCA Of Cancer_Human_Active",
     ylab = "Standard Deviation",
     xlab = "Component",
     ylim = c(0, 0.06))
```

```{r fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
biplot(pca_info)
```

From the biplot the most easily visible components are: {A, R, AA, V, D, L, I, Y, M, E, K, N, Q, S, C, P, G}

**NOTE:** It would be interesting to find the points which are PC2 > 0.06. This would be interesting to follow them along the modeling process and see if these are problems children.

Genereate data.frame for PC1:3
```{r}
Class_0_1 <- cancer_human_comps$Class
class_pc1_2_data <- as.data.frame(cbind(Class_0_1, pca_info$x[,1:3]))

# head(class_pc1_2_data)
tail(class_pc1_2_data)
```
Plot 'Class' vs 'PC1' and 'PC2' using principle component scores 
```{r fig.height=6, fig.width=7}
ggplot(class_pc1_2_data, aes(PC1, PC2, col = Class_0_1, fill = Class_0_1)) + 
    stat_ellipse(geom = "polygon", col = "black", alpha = 0.2) +
    geom_point(shape = 21, col = "black")
```
Plot 'Class' vs 'PC1' and 'PC3' Scores
```{r fig.height=6, fig.width=7}
ggplot(class_pc1_2_data, aes(PC1, PC3, col = Class_0_1, fill = Class_0_1)) + 
    stat_ellipse(geom = "polygon", col = "black", alpha = 0.2) +
    geom_point(shape = 21, col = "black")
```
Plot 'Class' vs 'PC2' and 'PC3' Scores
```{r fig.height=6, fig.width=7}
ggplot(class_pc1_2_data, aes(PC2, PC3, col = Class_0_1, fill = Class_0_1)) + 
    stat_ellipse(geom = "polygon", col = "black", alpha = 0.2) +
    geom_point(shape = 21, col = "black")
```

Correlations between variables and principle components
```{r}

cancer_human_PC1scores <- as.data.frame(cbind(cancer_human_Active, pca_info$x[,1]))



corr(cancer_human_PC1scores, cancer_human_PC1scores$792)
```









