---
title: "pca-dim-redux"
author: "MCC"
date: "8/29/2019"
output: html_document
---

Title:

Libraries  
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)

Libraries = c("readr", "knitr", "seqinr", "stringr", "doMC")

for(p in Libraries){ library(p, character.only = TRUE) }
```

FOR `doMC`

1. registerDoMC(cores = 3) # Start multi-processor mode
2. registerDOSEQ() # Stop multi-processor mode

## Formulate your questions

The purpose of the PCA is dimensionality reduction;

Q1. Can the number of features be reduced using PCA?

Import data
```{r}
cancer_human_comps <- read_csv("../1data/cancer_human_comps.csv",
                               col_types = cols(Class = col_factor(levels = c("0","1")), 
                                                PID = col_character()))
#View(cancer_human_comps)
```
Warning message: Missing column names filled in: 'X244' [244] <- "NA"

**NOTE: Column X244 should be marked "NA".  "NA" = Asparagine + Alanine**


**Pricipal Components Analysis with princomp**

PCA is very sensitive to large values and it is recommended that center and scaling or ranging be done. However the values are already {0 <= Values <= 1}
```{r}
#select the columns with the variables that you're conducting the PCA on
pca.active <- cancer_human_comps[,4:23]

fit_20aa <- princomp(pca.active, cor = TRUE) 
names(fit_20aa)
```
```{r}
fit_20aa
```
 
`cumsum(iPCA$sdev^2 / sum(iPCA$sdev^2))`
`plot(cumsum(iPCA$sdev^2$ / sum(iPCA$sdev^2)), type="b")`
```{r}
plot(cumsum(fit_20aa$sdev^2 / sum(fit_20aa$sdev^2)),
     ylim = c(0,1),
     type = "b")
```

```{r}
cumsum(fit_20aa$sdev^2 / sum(fit_20aa$sdev^2))
```

