---
title: "pca-dim-redux"
author: "MCC"
date: "8/29/2019"
output: html_document
---

Title:

Libraries  
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)

Libraries = c("readr", "knitr", "seqinr", "stringr", "doMC")

for(p in Libraries){ library(p, character.only = TRUE) }
```

FOR `doMC`

1. registerDoMC(cores = 3) # Start multi-processor mode
2. registerDOSEQ() # Stop multi-processor mode

## Formulate your questions

The purpose of the PCA is dimensionality reduction;

Q1. Can the number of features be reduced using PCA?

Import data
```{r}
cancer_human_comps <- read_csv("../1data/cancer_human_comps.csv",
                               col_types = cols(Class = col_factor(levels = c("0","1")), 
                                                PID = col_character()))
#View(cancer_human_comps)
```
Warning message: Missing column names filled in: 'X244' [244] <- "NA"

**NOTE: Column X244 should be marked "NA".  "NA" = Asparagine + Alanine**


**Pricipal Components Analysis with princomp**

```{r}
#select the columns with the variables that you're conducting the PCA on
pca_active <- cancer_human_comps[, 4:23]

pca_fit <- princomp(pca_active, cor = TRUE) 

summary(pca_fit) # print summary of components
```
Scree Plot
```{r}
plot(pca_fit, type="lines")
```


```{r}
#load more libraries
library(factoextra)
library(corrplot)

# Initialize the PCA with the prcomp() function
pca_prcomp <- prcomp(pca_active, scale = TRUE)

# Visualize the eigenvalues with a scree plot. 
fviz_eig(pca_prcomp, addlabels = TRUE, ylim = c(0,30))
```

```{r}
# Get the eigenvalues
eig.val <- get_eigenvalue(pca_prcomp)
eig.val
```

```{r}
res.var <- get_pca_var(pca_prcomp)
#res.var$contrib 
#res.var$cos2    

# Visualize Quality of Representation (cos2)
corrplot(res.var$cos2, is.corr=FALSE)
```


```{r}
# Visualize total quality of representation (cos2) of variables on Dim.1 and Dim.2 (axes=1:2)
fviz_cos2(pca_prcomp, 
          ylim = c(0,0.8),
          choice = "var", 
          axes = 1:2)
```


```{r}
eig.val$cumulative.variance.percent
plot(eig.val$cumulative.variance.percent,
     ylim = c(0,100),
     type = "b")
```

