---
title: "pca-dim-redux"
author: "MCC"
date: "8/29/2019"
output: html_document
---

Title:

Libraries  
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)

Libraries = c("readr", "knitr", "seqinr", "stringr", "doMC")

for(p in Libraries){ library(p, character.only = TRUE) }
```

FOR `doMC`

1. registerDoMC(cores = 3) # Start multi-processor mode
2. registerDOSEQ() # Stop multi-processor mode



## Formulate your questions

The purpose of the PCA is dimensionality reduction;

Q1. Can the number of features be reduced using PCA?

Import data
```{r}
cancer_human_comps <- read_csv("../1data/cancer_human_comps.csv",
                               col_types = cols(Class = col_factor(levels = c("0","1")), 
                                                PID = col_character()))
#View(cancer_human_comps)
```
Warning message: Missing column names filled in: 'X244' [244] <- "NA"

**NOTE: Column X244 should be marked "NA".  "NA" = Asparagine + Alanine**


**Pricipal Components Analysis with princomp**

PCA is very sensitive to large values and it is recommended that center and scaling or ranging be done. However the values are already {0 <= Values <= 1}
```{r}
#select the columns with the variables that you're conducting the PCA on
pca.active <- cancer_human_comps[,4:423]

fit <- princomp(pca.active, cor = TRUE) 
names(fit)
```
```{r}
fit$sdev  
```

cumsum(iPCA$sdev^2 / sum(iPCA$sdev^2)), 
plot(cumsum(iPCA$sdev^2 / sum(iPCA$sdev^2)), type="b")
```{r}
plot(cumsum(fit$sdev^2 / sum(fit$sdev^2)), type = "b")
```


```{r}
summary(fit) # print summary of components
```


```{r}

```


Scree Plot
```{r}
plot(fit,
     ylim = c(0, 25),
     type = "lines")  
```

```{r}
#load more libraries
library(factoextra)
library(corrplot)

# Initialize the PCA with the prcomp() function
pca_prcomp <- prcomp(na.omit(pca.active, scale = TRUE))

# Visualize the eigenvalues with a scree plot. 
fviz_eig(pca_prcomp, addlabels = TRUE, ylim = c(0, 25))
```

```{r}
# Get the eigenvalues
eig.val <- get_eigenvalue(pca_prcomp)
eig.val
```

Results for Variables
```{r}
res.var <- get_pca_var(pca_prcomp)
res.var$coord          # Coordinates
```



```{r}
res.var$contrib        # Contributions to the PCs
```



```{r}
res.var$cos2           # Quality of representation
```


Visualize Quality of Representation (cos2)
```{r}
corrplot(res.var$cos2, is.corr=FALSE)
```


```{r}
# Visualize total quality of representation (cos2) of variables on Dim.1 and Dim.2 (axes=1:2)
fviz_cos2(pca_prcomp, choice = "var", axes = 1:2)
```

```{r}
# Color by quality of representation values: quality on the factor map
fviz_pca_var(pca_prcomp, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
             )
```

`



```{r}
#cumulative scree plot
plot(cumsum(prop_varex), xlab = "Principal Component",
              ylab = "Cumulative Proportion of Variance Explained",
              type = "b")
```


